GSEA datasets for FDR benchmarking

### 2017-12-09 datasets/GSEA/gsea.Rmd

any( is.na(genes) )
stopifnot(!any(is.na(genes)))
pwf <- nullp(genes, bias.data=geneLength )
goRes <- goseq( pwf, gene2cat=goSets )

@@

@@

dplyr:::filter( goRes, numDEInCat > 0, numInCat > 15 ) %>%
  strat_hist( pval="over_represented_pvalue", covariate="numInCat", maxy=11)

@@

estimatePerformanceMetrics( sGSEA, alpha=0.1, tidy=TRUE ) %>%
  filter( blabel %in% c("lfdr","ihw-a10","bl-df03","qvalue","bh", "bonf") ) %>%
  select( blabel, value )

@@

getOverlapIndexes <- function( labs=c("lfdr", "ihw-a10"), alpha=0.1, sGSEA ){
  rowSums( assays(sGSEA)[["qvalue"]][,labs,drop=FALSE] < alpha) == length(labs) &
  !(rowSums( assays(sGSEA)[["qvalue"]][,c("lfdr","ihw-a10","bl-df03","qvalue","bh", "bonf")] < alpha, na.rm=TRUE ) > (length(labs)))
}

set1 <- getOverlapIndexes( c("lfdr", "ihw-a10"), alpha=0.1, sGSEA=sGSEA )
set2 <- getOverlapIndexes( c("bl-df03"), alpha=0.1, sGSEA=sGSEA )
set3 <- getOverlapIndexes( c("lfdr","ihw-a10","bl-df03","qvalue","bh"), alpha=0.1, sGSEA=sGSEA )

sizesDf <- data.frame( 
  size=c( rowData( sGSEA )$ind_covariate[which(set1)], 
          rowData( sGSEA )$ind_covariate[which(set2)], 
          rowData( sGSEA )$ind_covariate[which(set3)] ),
  label=rep(c("set1", "set2", "set3"), c(sum(set1), sum(set2), sum(set3)) ) )

>>>>

@@

rank_scatter( dat=goRes, pval="over_represented_pvalue", 
              covariate="numInCat", bins=50, funx=log2, 
              funfill=log10_trans()) +
    ylim(0, 12) + ggtitle("Over-represented gene sets") +
    xlab( expression(log[10]~"(# of genes)")) +
    ylab( expression(-log[10]~"(p-value)") ) 
```

@@

under_represented_pvalue
dplyr:::filter( goRes, numDEInCat > 0, numInCat > 10 ) %>%
  strat_hist( pval="over_represented_pvalue", covariate="numInCat", maxy=10)

@@

@@

methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots( sGSEA, alpha=0.1, nsets=6, methods=methods, trans=log2 )
